A basic obstruction-free queue is given in (*REF*). From this queue, the authors
construct a wait-free queue by using the fast-path-slow-path methodology.

$FAA(x, v)$ atomically reads the value stored in the $x$ variable, and
increments it by one. $CAS(x, t, v)$ atomically reads the value stored in $x$,
compares it to $t$ and, if $x$ is equal to $t$ (success), replaces the value of
$x$ by $v$. \\

\para{Basic queue} This queue is designed to be fast. It is neither wait-free or lock-free because
it is proned to livelocking. As only one thread is guaranteed to progress, this
queue is only obstruction-free. It uses a shared infinite array to store
elements. We will see later how memory can be reclaimed. Two special values are
reserved : $\bot$ (bottom) and $\top$ (top). $\bot$ stands for empty cells as
the queue is initially filled with $\bot$. $\top$ stands for unusable cells.
When one thread dequeues an element, he marks the cells with $\top$ to prevent
other threads to enqueue an element in it.

To enqueue an element, one thread try to find an available cell on the array, a
cell marked with $\bot$. One cannot enqueue an element in a $\top$ marked cell
because it could violate the FIFO property of the queue. To get an unique index
on the array, they uses fetch-and-add to increment the shared tail pointer.
Considering the pointer is shared by all threads, using compare-and-swap instead
of fetch-and-add would result in lots of failures. After one thread is given an
unique index, he needs to certify that the cell is empty. He then uses
compared-and-swap to enqueue an element into the array. In case of
compare-and-swap failure, redo the whole process until the element is enqueued.

The dequeue operation works in a similar manner, one thread try to find either a
cell filled with an element or with $\top$ by using fetch-and-add and a shared
head pointer. If a thread stops on a $\top$ marked cell, the dequeue returns
\texttt{EMPTY}.


\para{Fast-path-slow-path}

\para{Memory reclamation}
Memory reclamation is not easy because of ABA problem
memory reclemation for system without garbage collector
malloc is not non-blocking, own allocation mechanism or we allocate a pool of
cells for each thread : ABA problem = double width CAS (not universaly
available)

cleanup retired segments
update tail and head pointers
visit threads in reserve order
overhead ?
thread failure ?

\para{Wait-free guaranty}
idée de preuve wait-free et linearizable
